\documentclass{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\textheight=10in
\pagestyle{empty}
%\raggedbottom
\raggedright

%  \renewcommand{\encodingdefault}{cg}
  %\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }
% DEFINITIONS FOR RESUME
\newcommand{\area}[2]{\vspace*{-9pt} \begin{verse}\textbf{#1}   #2 \end{verse}  }
\newcommand{\lineunder}{\vspace*{-8pt} \\ \hspace*{-18pt} \hrulefill \\}
\newcommand{\header}[1]{{\hspace*{-15pt}\vspace*{6pt} \textsc{#1}} \vspace*{-6pt} \lineunder}
\newcommand{\employer}[3]{{ \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }}
\newcommand{\contact}[3]{
\vspace*{-8pt}
\begin{center}
{\huge \scshape {#1}}\\
#2  
#3
\end{center}
\vspace*{-8pt}
}
\newenvironment{achievements}{\begin{list}{$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}\end{list}}
\newcommand{\schoolwithcourses}[4]{
 \textbf{#1} #2 $\bullet$ #3\\ 
#4 $\bullet$  Selected Coursework:\\
\vspace*{5pt}
}
\newcommand{\school}[4]{
 \textbf{#1} #2 $\bullet$ #3\\ 
#4 \\
}
% END RESUME DEFINITIONS

\begin{document}

\small
\smallskip
\vspace*{-44pt}


\begin{center}
 
\huge Matthew Robert Walters 
\linebreak
\normalsize

{1810A Webster Street, San Francisco CA 94115 $\bullet$ (559) 859-6361 $\bullet$ matthewrobertwalters@gmail.com} \newline


 \textit{Skiing and Software}
\end{center}

\small

\header{Skills}

\begin{description}

\item[Languages] Ruby$^3$, Javascript$^3$, Java$^3$, Bash$^3$, Python$^2$, Scala$^2$, Lua$^1$, C/C++$^1$, \LaTeX$^1$             \hfill Basic - 1

\item[Tools] Rails$^3$, Git$^3$, Rspec$^3$, Capybara$^3$, Nginx$^2$, HAProxy$^2$, Ansible$^2$, Jenkins$^2$, React$^2$, Docker$^2$     \hfill Intermediate - 2	
			                                            
\item[Data Store] MySql$^3$, Postgres$^3$, Redis$^3$, Elasticsearch$^3$, MongoDB$^2$                                                       \hfill Advanced - 3

\end{description}

\header{Work History}

	\begin{description}
	
	 \item \textbf{Shopkeepery $|$ Founder $|$ Mar 2016 - Present} \\
	 \textit{
	 Starting as a side project, Shopkeepery is a small business I've built to help artists sell art. 
	 Shopkeepery has been a tremendous experience allowing me to refine and temper skills as an entrepreneur, product designer, marketer, and software engineer.
	 }
	 
	 \item$\bullet$ Developed simple and scalable backend architecture with Ansible, Nginx, and HAProxy on AWS.
	 \item$\bullet$ Developed simple UI for artists to design products quickly and easily.
	 
	 \item$\bullet$ Supports scalable uploading of very high-resolution image files.
	 \item$\bullet$ Deployed by a continuous integration pipeline with RSpec, Ansible, and CircleCI
	 \item$\bullet$ Built custom domain support for shops with SSL certs served dynamically with Nginx, Lua, Postgres.
	 \item$\bullet$ Created integration with Facebook Marketing API to export collections of products as Facebook ads.
	 \item$\bullet$ Created robust image manipulation pipeline with Sidekiq and Imagemagick.
	
	 \item \textbf{Swiftype $|$ Software Engineer $|$ May 2014 - Mar 2016} \\
	 \textit{Swiftype delivers search as a service for everyone from small business to large enterprise corporations.}
	 
	 \item$\bullet$ Maintained API serving 3 billion requests per month with average response times below 200ms.
	 \item$\bullet$ Worked with TechOps lead to migrate 800GB MongoDB instance to sharded MySql solution.
	 \item$\bullet$ Integrated our sales and marketing stack including SalesForce, Pardot, GA, Mixpanel, Olark, and Slack.
	 \item$\bullet$ Maintained and extended a proprietary multi-tenant highly scalable web crawler built with JRuby.
	 \item$\bullet$ Worked extensively with Elasticsearch to optimize search results across thousands of websites.
	 \item$\bullet$ Developed and supported multiple 3rd party javascript libraries running in millions of browsers.
	 \item$\bullet$ Interviewed over 150 applicants for engineering positions and optimized recruitment pipeline. 
	
	 \item \textbf{Couchsurfing $|$ Analytics Engineer $|$ Oct 2012 - Oct 2013} \\
	  \textit{Couchsurfing is a social network allowing users to find accomodations, activities, and companions while traveling.}
	 \item$\bullet$ Responsible for designing and implementing analytics infrastructure for site serving 7.3 million users.
	 \item$\bullet$ Conducted cohort analysis and A/B testing to measure performance of all new features.
	 \item$\bullet$ Supported product team in feature design with bespoke data analysis and visualization.
	 
	 
	\end{description}

\header{Side Projects and Extra Curricular Activities}

\begin{description}
 \item \textbf{Software Mentorship $|$ Passion } \\

 \textit{I am very passionate about teaching. }  
 \item$\bullet$ Developed simple lesson plans for beginning bash, python, and ruby students.
 \item$\bullet$ Developed simple lesson plans for beginning bash, python, and ruby students.
 
 \item \textbf{Nantucket $|$ Limerick Generation Framework $|$ GitHub Project: github.com/mattwalters/nantucket } \\
 \textit{A Python framework for implementing limerick generation strategies. The framework lazily creates and memoizes computationally expensive lexical resources.}
 \item$\bullet$ Provides useful lexical resources including a rhyming dictionary and an n-gram graph generator.
 \item$\bullet$ Implemented a limerick generation strategy that uses Markov chains via n-gram graph traversal.
 
\end{description}


\header{Education}
\begin{description}
 \item \textbf{University of California, Berkeley $|$ 2007 - 2012}
 \item$\bullet$ Bachelor of Science, Environmental Economics and Policy
 \item$\bullet$ Bachelor of Arts, Anthropology
 \begin{center}
\textit{Selected Coursework}
 \item {Structure and Interpretation of Computer Programs} $\bullet$ {Data Structures and Object Oriented Programming}
 {Machine Structures} $\bullet$ {Algorithms} $\bullet$ {Modeling Biological Resources} $\bullet$ {Business Organization and Contract Law}
 {Economics of Innovation and Intellectual Property} $\bullet$ {Language and the Brain}
 
 \end{center}
 
\end{description}



\end{document}
