\documentclass{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\textheight=10in
\pagestyle{empty}
%\raggedbottom
\raggedright

%  \renewcommand{\encodingdefault}{cg}
  %\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }
% DEFINITIONS FOR RESUME
\newcommand{\area}[2]{\vspace*{-9pt} \begin{verse}\textbf{#1}   #2 \end{verse}  }
\newcommand{\lineunder}{\vspace*{-8pt} \\ \hspace*{-18pt} \hrulefill \\}
\newcommand{\header}[1]{{\hspace*{-15pt}\vspace*{6pt} \textsc{#1}} \vspace*{-6pt} \lineunder}
\newcommand{\employer}[3]{{ \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }}
\newcommand{\contact}[3]{
\vspace*{-8pt}
\begin{center}
{\huge \scshape {#1}}\\
#2  
#3
\end{center}
\vspace*{-8pt}
}
\newenvironment{achievements}{\begin{list}{$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}\end{list}}
\newcommand{\schoolwithcourses}[4]{
 \textbf{#1} #2 $\bullet$ #3\\ 
#4 $\bullet$  Selected Coursework:\\
\vspace*{5pt}
}
\newcommand{\school}[4]{
 \textbf{#1} #2 $\bullet$ #3\\ 
#4 \\
}
% END RESUME DEFINITIONS

\begin{document}

\small
\smallskip
\vspace*{-44pt}


\begin{center}
 
\huge Matthew Robert Walters 
\linebreak
\normalsize

{3005 23rd St., San Francisco CA, 94110 $\bullet$ +1 (415) 613-1439 $\bullet$ mattrwal@gmail.com} \newline

 \textit{Passionate about building products from conception to product-market fit}
\end{center}

\small

\header{Skills}

\begin{description}

\item[Languages] Ruby$^4$, Javascript$^4$, Typescript$^3$, Bash$^2$, Python$^2$, Scala$^1$, C/C++$^1$, \LaTeX$^1$              \hfill Basic - 1

\item[Tools] Rails$^4$, React$^4$, Git$^4$, GraphQL$^4$, MUI$^4$, Rspec$^4$, Node$^3$, Cypress$^3$, Prisma$^2$, Tailwind CSS$^1$     \hfill Proficient - 2	
\item[Infrastructure] Heroku$^4$, Docker$^4$, AWS$^3$, CircleCI$^3$, Nginx$^3$, Ansible$^2$                  \hfill Advanced - 3

			                                            
\item[Data Stores] Postgres$^4$, Redis$^4$, Elasticsearch$^3$, MySql$^2$, MongoDB$^2$                  \hfill Expert - 4                                  

\end{description}

\header{Work History}

	\begin{description}
	
	 \item \textbf{Perfect Venue | perfectvenue.com | Cofounder \& CTO | Mar 2020 - Jan 2023} \\
	 \textit{Perfect Venue is a VC backed CRM for restaurants and venues that host private events.}
	 \item$\bullet$ Built feature rich events platform that grew to 1000+ users and \$500,000 ARR during Covid pandemic.
	 	  \item$\bullet$ Educated and communicated with non-technical cofounder about software development process.

	 \item$\bullet$ Sourced, interviewed, and hired founding team of engineers and developed early engineering culture.

	  	 \item$\bullet$ Integrated Stripe and Finix to allow users to make charges through the product at a \$90 million annual run rate.
	 \item$\bullet$ Designed and built email relay system on SendGrid to provide integrated messaging capability on the platform.
	 \item$\bullet$ Automated data migration from primary competitors to facilitate white glove onboarding.
	
	 \item \textbf{Remote Year | remoteyear.com | Senior Software Engineer | Jan 2017 - Feb 2020} \\
	 \textit{Remote Year provides work-travel adventures around the world to location independent workers.}
	 \item$\bullet$ Responsible for designing, implementing, and maintaining all software for entire organization.
	 \item$\bullet$ Migrated core operational data from google sheets to Postgres based web app with 0 downtime.
	 \item$\bullet$ Empowered team members on every team with streamlined processes and automations.
	 \item$\bullet$ Built reliable custom invoicing process on Stripe that processes tens of millions of dollars per year.
	 \item$\bullet$ Heavily support product, sales, and marketing teams with data collection and analysis.
	
	 \item \textbf{Shopkeepery | Founder | Mar 2016 - Dec 2016} \\
	 \textit{Starting as a side project, Shopkeepery was an application to help artists sell art.}
	 
	 \item$\bullet$ Architected simple and scalable backend with Ansible, Nginx, and HAProxy on AWS.
	 \item$\bullet$ Deployed by a continuous integration pipeline with RSpec, Ansible, and CircleCI.
	 \item$\bullet$ Built custom domain support with Let’s Encrypt SSL certs served dynamically with Nginx, Lua, Postgres.
	 \item$\bullet$ Created integration with Facebook Marketing API to export collections of products as Facebook ads.
	 \item$\bullet$ Designed robust image manipulation pipeline with Sidekiq and Imagemagick.
	
	 \item \textbf{Swiftype | swiftype.com | Software Engineer | May 2014 - Mar 2016} \\
	 \textit{Swiftype delivers search as a service for everyone from small business to large enterprises.}
	 
	 \item$\bullet$ Maintained API serving 3 billion requests per month with average response times below 200ms.
	 \item$\bullet$ Worked with TechOps lead to migrate 800GB MongoDB instance to a sharded MySql solution.
	 \item$\bullet$ Integrated our sales and marketing stack including SalesForce, Pardot, GA, Mixpanel, Olark, and Slack.
	 \item$\bullet$ Supported multiple 3rd party javascript libraries running in millions of browsers.
	 	
	 \item \textbf{Couchsurfing | couchsurfing.com | Analytics Engineer | Oct 2012 - Oct 2013} \\
	  \textit{Couchsurfing is a social network allowing users to find accommodations and activities while traveling.}
	 \item$\bullet$ Responsible for designing and implementing analytics infrastructure for site serving 7.3 million users.
	 \item$\bullet$ Conducted cohort analysis and A/B testing to measure performance of all new features to inform product team.
	 
	 
	\end{description}


\header{Education}
\begin{description}
 \item \textbf{University of California, Berkeley $|$ 2007 - 2012}
 \item$\bullet$ Bachelor of Science, Environmental Economics and Policy
 \item$\bullet$ Bachelor of Arts, Anthropology
 \begin{center}
\textit{Selected Coursework}
 \item {Structure and Interpretation of Computer Programs} $\bullet$ {Data Structures and Object Oriented Programming}
 {Machine Structures} $\bullet$ {Algorithms} $\bullet$ {Modeling Biological Resources} $\bullet$ {Business Organization and Contract Law}
 {Economics of Innovation and Intellectual Property} $\bullet$ {Language and the Brain}
 
 \end{center}
 
\end{description}



\end{document}
